---
title: "Workflow ProbODER LSODA"
author: "Claire Descombes"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: styles.css
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=6)
```

```{r, echo=FALSE, include=FALSE}
# Set source directory
source_directory <- '~/Documents/GitHub/proboder/Functions/'

# Source necessary functions
source(file.path(source_directory, 'LSODA.R'))
source(file.path(source_directory, 'initialization.R'))
source(file.path(source_directory, 'inference.R'))
source(file.path(source_directory, 'processing_saving_loading.R'))
source(file.path(source_directory, 'scoring.R'))
source(file.path(source_directory, 'plotting.R'))
source(file.path(source_directory, 'random_search.R'))

# Load or install necessary packages
load_required_packages()
```

## Simulation Example

#### Simulate data

```{r, fig.width=8, fig.height=6}
# --------------
# Initialization
# --------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# ------------------------
# Simulation of a data set
# ------------------------

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
if (noise > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

l <- 9 # lengthscale
noise_wiener_X <- 50 # noise of the Wiener process associated with X
noise_wiener_U <- 0.01 # noise of the Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise,
                   noise_X = sqrt(noise), noise_U = 0.01,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results,grids)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(contact_rate_with_CI <- plot_contact_rate_with_CI(U_plot = U_plot, 
                          df_beta = df_beta, # if available, otherwise set NULL
                          latency_rate = lambda, 
                          recovery_rate = gamma, 
                          fatality_rate = eta, 
                          lengthscale = l))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# If wished, a random search on a set of parameters can be performed.

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(6, 15, by = 0.5)
  seq_wiener_X <- seq(1, 30, by = 0.5)
  seq_wiener_U <- seq(0.001, 1, by = 0.01)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)
  seq_clip_X <- c(1, 10, 100)
  seq_clip_U <- c(0.01, 0.1)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise = noise, lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit,
      seq_clip_X = seq_clip_X,
      seq_clip_U = seq_clip_U
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 4))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 4))
  
  # If desired, save the plot using ggsave
  if (FALSE) { # set TRUE to save plot
    output_dir <- 
      '~/Documents/GitHub/proboder/Results/2024-07-29_16-20-27-examples/'
  ggsave(filename = file.path(output_dir, 'grid_search_means.png'),
         plot = grid_of_mean_plots,
         bg = "white",
         width = 8,
         height = 6)
  ggsave(filename = file.path(output_dir, 'grid_search_medians.png'),
         plot = grid_of_median_plots,
         bg = "white",
         width = 8,
         height = 6)
  }
  
  (best_params <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

Same data set, parameters given by random search.

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

# Results random search:
# > best_params
#    l noise_wiener_X noise_wiener_U beta0prime jit clip_X clip_U
# 1 12              2          0.101        0.5 0.1      1   0.01

l <- 12 # lengthscale
noise_wiener_X <- 2 # noise of the Wiener process associated with X
noise_wiener_U <- 0.101 # noise of the Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0.5 # starting 1st derivative of transmission rate
jit <- 0.1 # value for jitter on innovation covariance
clip_X <- 1 # value to clip variance of X
clip_U <- 0.01 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise,
                   noise_X = sqrt(noise), noise_U = 0.01,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results,grids)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- plot_compartments_separately(model = model,
                                          obs = obs,
                                          obs_with_noise = NULL, # if available, otherwise set NULL
                                          X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(contact_rate_with_CI <- plot_contact_rate_with_CI(U_plot = U_plot, 
                          df_beta = df_beta, # if available, otherwise set NULL
                          latency_rate = lambda, 
                          recovery_rate = gamma, 
                          fatality_rate = eta, 
                          lengthscale = l))
```

## Simulation A

With D compartment.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# --------------
# Initialization
# --------------

model <- 'SEIRD' # model to be simulated 
                 # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# ------------------------
# Simulation of a data set
# ------------------------

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
if (noise > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

l <- 12 # lengthscale
noise_wiener_X <- 2 # noise of the Wiener process associated with X
noise_wiener_U <- 0.101 # noise of the Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0.5 # starting 1st derivative of transmission rate
jit <- 0.1 # value for jitter on innovation covariance
clip_X <- 1 # value to clip variance of X
clip_U <- 0.01 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise,
                   noise_X = sqrt(noise), noise_U = 0.01,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results,grids)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- plot_compartments_separately(model = model,
                                          obs = obs,
                                          obs_with_noise = NULL, # if available, otherwise set NULL
                                          X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(contact_rate_with_CI <- plot_contact_rate_with_CI(U_plot = U_plot, 
                          df_beta = df_beta, # if available, otherwise set NULL
                          latency_rate = lambda, 
                          recovery_rate = gamma, 
                          fatality_rate = eta, 
                          lengthscale = l))
```

## Simulation B

Giving only R compartment to observe.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# --------------
# Initialization
# --------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# ------------------------
# Simulation of a data set
# ------------------------

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
if (noise > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

# Results random search:
# > best_params
#   l noise_wiener_X noise_wiener_U beta0prime  jit clip_X clip_U
# 1 6            5.8           0.01      -0.25 0.01      1    0.1

l <- 6 # lengthscale
noise_wiener_X <- 5.8 # noise of the Wiener process associated with X
noise_wiener_U <- 0.01 # noise of the Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- -0.25 # starting 1st derivative of transmission rate
jit <- 0.01 # value for jitter on innovation covariance
clip_X <- 1 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise_only_R # choose if obs, obs_with_noise,        
                                    # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise,
                   noise_X = sqrt(noise), noise_U = 0.01,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results,grids)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- plot_compartments_separately(model = model,
                                          obs = obs,
                                          obs_with_noise = NULL, # if available, otherwise set NULL
                                          X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(contact_rate_with_CI <- plot_contact_rate_with_CI(U_plot = U_plot, 
                          df_beta = df_beta, # if available, otherwise set NULL
                          latency_rate = lambda, 
                          recovery_rate = gamma, 
                          fatality_rate = eta, 
                          lengthscale = l))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# If wished, a random search on a set of parameters can be performed.

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(1, 15, by = 0.5)
  seq_wiener_X <- seq(0.1, 10, by = 0.1)
  seq_wiener_U <- seq(0.01, 1, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)
  seq_clip_X <- c(1, 10, 100)
  seq_clip_U <- c(0.1, 0.2, 0.5)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise = noise, lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit,
      seq_clip_X = seq_clip_X,
      seq_clip_U = seq_clip_U
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 4))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 4))
  
  # If desired, save the plot using ggsave
  if (FALSE) { # set TRUE to save plot
    output_dir <- 
      '~/Documents/GitHub/proboder/Results/2024-07-29_16-20-27-examples/'
  ggsave(filename = file.path(output_dir, 'grid_search_means.png'),
         plot = grid_of_mean_plots,
         bg = "white",
         width = 8,
         height = 6)
  ggsave(filename = file.path(output_dir, 'grid_search_medians.png'),
         plot = grid_of_median_plots,
         bg = "white",
         width = 8,
         height = 6)
  }
  
  (best_params <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

## Simulation C

More days, testing phase.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# --------------
# Initialization
# --------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 100 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){0.2*cos(t/10)+0.6} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# ------------------------
# Simulation of a data set
# ------------------------

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
if (noise > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

# Results random search:
# > best_params
#     l noise_wiener_X noise_wiener_U beta0prime   jit clip_X clip_U    
# 1 124            1.6          0.001       0.25 0.001     10    0.1

l <- 124 # lengthscale
noise_wiener_X <- 1.6 # noise of the Wiener process associated with X
noise_wiener_U <- 0.001 # noise of the Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0.25 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise,
                   noise_X = sqrt(noise), noise_U = 0.01,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = 499985, start_E = 5, 
                   start_I = 5, start_R = 5,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results,grids)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(contact_rate_with_CI <- plot_contact_rate_with_CI(U_plot = U_plot, 
                          df_beta = df_beta, # if available, otherwise set NULL
                          latency_rate = lambda, 
                          recovery_rate = gamma, 
                          fatality_rate = eta, 
                          lengthscale = l))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# If wished, a random search on a set of parameters can be performed.

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(115, 130, by = 0.1)
  seq_wiener_X <- seq(1, 5, by = 0.2)
  seq_wiener_U <- seq(0.001, 0.5, by = 0.005)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1)
  seq_clip_X <- c(1, 10, 100)
  seq_clip_U <- c(0.1, 0.2, 0.5)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise = noise, lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit,
      seq_clip_X = seq_clip_X,
      seq_clip_U = seq_clip_U
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 4))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 4))
  
  # If desired, save the plot using ggsave
  if (FALSE) { # set TRUE to save plot
    output_dir <- 
      '~/Documents/GitHub/proboder/Results/2024-07-29_16-20-27-examples/'
  ggsave(filename = file.path(output_dir, 'grid_search_means.png'),
         plot = grid_of_mean_plots,
         bg = "white",
         width = 8,
         height = 6)
  ggsave(filename = file.path(output_dir, 'grid_search_medians.png'),
         plot = grid_of_median_plots,
         bg = "white",
         width = 8,
         height = 6)
  }
  
  (best_params <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

--------------------------------------------------------------------------------

## Store data

```{r}
# If wished, the processed data can be stored
directory_save <- '~/Documents/GitHub/proboder/Results/'
if (TRUE) { # Set TRUE to save
  save_processed_data(inference_results = inference_results, 
                      processed_data = processed_data, 
                      directory = directory_save,
                      simulated_compartments = simulated_compartments, 
                      simulated_beta = simulated_beta,
                      compartments = compartments,
                      contact_rate_with_CI = contact_rate_with_CI,
                      grid_plots_sep = grid_plots_sep,
                      styled_table = styled_table)
}

# To store the table as a png file, use the manual export option from the viewer.
# Save in size 400x200.
```