---
title: "Workflow ProbODER LSODA"
author: "Claire Descombes"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: styles.css
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=6)
```

## Import functions

```{r, echo=FALSE, include=FALSE}
# Set source directory
source_directory <- '~/Documents/GitHub/proboder/Functions/'

# Source necessary functions
source(file.path(source_directory, 'LSODA.R'))
source(file.path(source_directory, 'initialization.R'))
source(file.path(source_directory, 'inference.R'))
source(file.path(source_directory, 'processing_saving_loading.R'))
source(file.path(source_directory, 'scoring.R'))
source(file.path(source_directory, 'plotting.R'))
source(file.path(source_directory, 'random_search.R'))

# Load or install necessary packages
load_required_packages()
```


#-------------------------------------------------------------------------------

## Simulation Example (simEx)

#### Simulate data

```{r, fig.width=8, fig.height=6}
# ------------------------
# Simulation of a data set
# ------------------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise_obs <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise_obs,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
df_R <- sim$df_R
if (noise_obs > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_R <- plots$simulated_R)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 9 # lengthscale
noise_wiener_X <- 50 # noise of Wiener process associated with X
noise_wiener_U <- 0.01 # noise of Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- NULL # 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# -------------
# Random search
# -------------

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(1, 100, by = 1)
  seq_wiener_X <- seq(1, 1000, by = 10)
  seq_wiener_U <- seq(0.001, 2, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise_obs = noise_obs, 
      lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0, clip_X = clip_X, clip_U = clip_U,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 3))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 3))
  
  (best_params_table <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

#### Perform inference with best parameters from random search

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 48 # lengthscale
noise_wiener_X <- 1 # noise of Wiener process associated with X
noise_wiener_U <- 1.521 # noise of Wiener process associated with U
beta0prime <- 0.25 # starting 1st derivative of transmission rate
jit <- 0.1 # value for jitter on innovation covariance

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```







## Simulation A (simA)

With D compartment.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# ------------------------
# Simulation of a data set
# ------------------------

model <- 'SEIRD' # model to be simulated 
                 # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise_obs <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise_obs,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
df_R <- sim$df_R
if (noise_obs > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_R <- plots$simulated_R)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 9 # lengthscale
noise_wiener_X <- 50 # noise of Wiener process associated with X
noise_wiener_U <- 0.01 # noise of Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# -------------
# Random search
# -------------

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(1, 100, by = 1)
  seq_wiener_X <- seq(1, 1000, by = 10)
  seq_wiener_U <- seq(0.001, 2, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise_obs = noise_obs, 
      lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0, clip_X = clip_X, clip_U = clip_U,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 3))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 3))
  
  (best_params_table <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

#### Perform inference with best parameters from random search

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 62 # lengthscale
noise_wiener_X <- 11 # noise of Wiener process associated with X
noise_wiener_U <- 0.341 # noise of Wiener process associated with U
beta0prime <- 0.5 # starting 1st derivative of transmission rate
jit <- 0.01 # value for jitter on innovation covariance

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```










## Simulation B (simB)

Giving only R compartment to observe.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# ------------------------
# Simulation of a data set
# ------------------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 30 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){2*cos(t/30)-1} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise_obs <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise_obs,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
df_R <- sim$df_R
if (noise_obs > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_R <- plots$simulated_R)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ------------------------
# Inference
# ------------------------

l <- 9 # lengthscale
noise_wiener_X <- 50 # noise of Wiener process associated with X
noise_wiener_U <- 0.01 # noise of Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise_only_R # choose if obs, obs_with_noise,        
                                    # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# -------------
# Random search
# -------------

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(1, 100, by = 1)
  seq_wiener_X <- seq(1, 1000, by = 10)
  seq_wiener_U <- seq(0.001, 2, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)
  
  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise_obs = noise_obs, 
      lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0, clip_X = clip_X, clip_U = clip_U,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 3))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 3))
  
  (best_params_table <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

#### Perform inference with best parameters from random search

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 42 # lengthscale
noise_wiener_X <- 141 # noise of Wiener process associated with X
noise_wiener_U <- 0.021 # noise of Wiener process associated with U
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 1 # value for jitter on innovation covariance

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```









## Simulation C (simC)

More days, different transmission rate.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# ------------------------
# Simulation of a data set
# ------------------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 80 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){0.2*cos(t/10)+0.6} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise_obs <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise_obs,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
df_R <- sim$df_R
if (noise_obs > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_R <- plots$simulated_R)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 124 # lengthscale
noise_wiener_X <- 1.6 # noise of Wiener process associated with X
noise_wiener_U <- 0.001 # noise of Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# -------------
# Random search
# -------------

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(100, 150, by = 0.5)
  seq_wiener_X <- seq(1, 10, by = 0.5)
  seq_wiener_U <- seq(0.001, 2, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)

  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise_obs = noise_obs, 
      lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0, clip_X = clip_X, clip_U = clip_U,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 3))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 3))
  
  (best_params_table <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

#### Perform inference with best parameters from random search

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 146 # lengthscale
noise_wiener_X <- 3 # noise of Wiener process associated with X
noise_wiener_U <- 0.021 # noise of Wiener process associated with U
beta0prime <- -0.25 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```




## Simulation D (simD)

Same as simC but giving access only to R.

#### Simulate data

```{r, fig.width=8, fig.height=6}
# ------------------------
# Simulation of a data set
# ------------------------

model <- 'SEIR' # model to be simulated 
                # ('SEIRD' or 'SEIR' available)

steps <- 1 # steps for time grid
max_time <- 80 # max time for time grid

lambda <- 1/(2.6) # latency rate, ref value 1/(2.6)
gamma <- 1/(2.6) # recovery rate, ref value 1/(2.6)
if (model == 'SEIRD') {
  eta <- 0.024*(1/15) # fatality rate, ref value 0.024*(1/15)
} else if (model == 'SEIR') {
  eta <- 0
}

beta <- function(t){0.2*cos(t/10)+0.6} # function for transmission rate

# Starting compartment counts
if (model == 'SEIRD') {
  xstart <- c(S = 499980, E = 5, I = 5, R = 5, D = 5)
} else if (model == 'SEIR') {
  xstart <- c(S = 499985, E = 5, I = 5, R = 5)
}
pop <- sum(xstart)

noise_obs <- 10 # noise to add on the data
            # set > 0 to avoid numerical instabilities
seed <- 5 # any integer, for reproducibility 
          # (set NA for no seed)

# Data simulation
sim <- simulate_data_LSODA(
    model = model,
    noise = noise_obs,
    seed = seed,
    steps = steps,
    max_time = max_time,
    lambda = lambda, gamma = gamma, eta = eta,
    pop = pop, 
    beta = beta,
    xstart = xstart)

# Get simulated data sets
obs <- sim$obs
df_beta <- sim$df_beta
df_R <- sim$df_R
if (noise_obs > 0) {
  obs_with_noise <- sim$obs_with_noise
}
obs_with_noise_only_R <- 
  obs_with_noise %>% select(t, R)

# Visualization
plots <- plotting_simulated_data_lsoda(
  model = model,
  sim = sim,
  latency_rate = lambda,
  recovery_rate = gamma,
  fatality_rate = eta,
  log = TRUE)

(simulated_beta <- plots$simulated_beta)
(simulated_R <- plots$simulated_R)
(simulated_compartments <- plots$simulated_compartments)
```

#### Perform inference

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 124 # lengthscale
noise_wiener_X <- 1.6 # noise of Wiener process associated with X
noise_wiener_U <- 0.001 # noise of Wiener process associated with U
beta0 = df_beta$beta[1] # starting transmission rate
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 0.001 # value for jitter on innovation covariance
clip_X <- 10 # value to clip variance of X
clip_U <- 0.1 # value to clip variance of U
obs_to_use <- obs_with_noise_only_R # choose if obs, obs_with_noise,        
                             # obs_with_noise_only_R

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```

#### Perform random search 

```{r, fig.width=8, fig.height=6}
# -------------
# Random search
# -------------

if (TRUE) { # set TRUE to perform random search
  seed <- 5
  num_param_sets <- 1000 # number of parameter sets to sample
  
  seq_l <- seq(100, 150, by = 0.5)
  seq_wiener_X <- seq(1, 10, by = 0.5)
  seq_wiener_U <- seq(0.001, 2, by = 0.02)
  seq_beta0prime <- c(-0.5, -0.25, 0, 0.25, 0.5)
  seq_jit <- c(0.001, 0.01, 0.1, 1)

  results_summary <- 
    run_random_search(
      model = model, obs_to_use = obs_to_use, df_beta = df_beta, 
      noise_obs = noise_obs, 
      lambda = lambda, gamma = gamma, eta = eta, pop = pop, 
      beta0 = beta0, clip_X = clip_X, clip_U = clip_U,
      seed = seed, num_param_sets = num_param_sets, 
      seq_l = seq_l, 
      seq_wiener_X = seq_wiener_X, 
      seq_wiener_U = seq_wiener_U, 
      seq_beta0prime = seq_beta0prime,
      seq_jit = seq_jit
    )

  plots_scores <- plot_scores(results_summary)
  invisible(grid_of_mean_plots <- grid.arrange(
    grobs = plots_scores$mean_plots,
    ncol = 2, 
    nrow = 3))
  invisible(grid_of_median_plots <- grid.arrange(
    grobs = plots_scores$median_plots,
    ncol = 2, 
    nrow = 3))
  
  (best_params_table <- find_best_hyperparameters(results_summary))
}

# Note that the random search runs even if errors are raised. 
# The number of errors is given at the end of the search.
```

#### Perform inference with best parameters from random search

```{r, fig.width=8, fig.height=6}
# ---------
# Inference
# ---------

l <- 138 # lengthscale
noise_wiener_X <- 8 # noise of Wiener process associated with X
noise_wiener_U <- 0.081	 # noise of Wiener process associated with U
beta0prime <- 0 # starting 1st derivative of transmission rate
jit <- 1 # value for jitter on innovation covariance

# Initialize
initial_params <-
    initialization(model = model, obs = obs_to_use,
                   beta0 = beta0, beta0prime = beta0prime,
                   lambda = lambda, gamma = gamma, eta = eta,
                   l = l, scale = 1, noise_obs = noise_obs,
                   noise_X = sqrt(noise_obs), noise_U = 0.1,
                   noise_wiener_X = noise_wiener_X, 
                   noise_wiener_U = noise_wiener_U,
                   pop = pop,
                   start_S = NULL, start_E = NULL, 
                   start_I = NULL, start_R = NULL,
                   start_D = NULL)

# Generate time grids for inference
grids <- generate_grid(obs, num_points_between = 0)

# Run inference
inference_results <- inference(model = model, 
                               grids = grids, 
                               obs = obs_to_use, 
                               jit = jit, 
                               clip_X = clip_X, clip_U = clip_U,
                               initial_params = initial_params)

# Process data for scoring and visualization
processed_data <- process_data(inference_results = inference_results,
                               grids = grids,
                               model = model,
                               pop = pop, 
                               lambda = lambda, 
                               gamma = gamma, 
                               eta = eta)
U_plot <- processed_data$U_plot
X_plot <- processed_data$X_plot
R_plot <- processed_data$R_plot
cond_plot <- processed_data$cond_plot

# Compute and display scores
(styled_table <- 
    compute_scores_and_table(U_plot = U_plot, df_beta = df_beta))

# Plot compartment counts inferred from simulated data
(compartments <- 
  plot_compartments(model = model,
     obs = obs, 
     obs_with_noise = obs_with_noise, # if available, otherwise set NULL
     X_plot = X_plot))

# Plot compartment counts separately
plots_sep <- 
  plot_compartments_separately(
    model = model,
    obs = obs,
    obs_with_noise = NULL, # if available, otherwise set NULL
    X_plot = X_plot)

num_plots <- length(plots_sep)
invisible(grid_plots_sep <- grid.arrange(
    grobs = plots_sep,
    ncol = 2,
    nrow = ceiling(num_plots/2)))

# Plot transmission rate with 95% confidence interval
(transmission_rate_with_CI <- 
    plot_transmission_rate_with_CI(U_plot = U_plot, 
    df_beta = df_beta, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot reproduction number with approx. 95% confidence interval
(reproduction_number_with_CI <- 
    plot_reproduction_number_with_CI(R_plot = R_plot, 
    df_R = df_R, # if available, otherwise set NULL
    latency_rate = lambda, 
    recovery_rate = gamma, 
    fatality_rate = eta, 
    lengthscale = l))

# Plot condition numbers of the innovation covariances 
# and covariance matrices
cond_plots <- 
    plot_condition_numbers(cond_plot)

number_plots <- length(cond_plots)
invisible(condition_numbers <- grid.arrange(
    grobs = cond_plots,
    ncol = 2,
    nrow = ceiling(number_plots/2)))
```






# -----------------------------------------------------------------------------

## Store data

```{r}
# -------------
# Store results
# -------------

# Every argument except directory is optional. If not available: set NULL.

directory_save <- '~/Documents/GitHub/proboder/Results/'
if (TRUE) { # Set TRUE to save
  save_processed_data(
    directory = directory_save,
    folder_name = 'simDRS',
    # Data
    inference_results = inference_results, 
    processed_data = processed_data, 
    # Plots
    simulated_compartments = simulated_compartments, 
    simulated_beta = simulated_beta,
    simulated_R = simulated_R,
    compartments = compartments,
    transmission_rate_with_CI = transmission_rate_with_CI,
    reproduction_number_with_CI = reproduction_number_with_CI,
    grid_plots_sep = grid_plots_sep,
    condition_numbers = condition_numbers,
    styled_table = styled_table,
    # Random search
    grid_of_mean_plots = grid_of_mean_plots,
    grid_of_median_plots = grid_of_median_plots,
    best_params_table = best_params_table,
    # Size
    plot_width = 8,
    plot_height = 6)
}

# To store a table as a png file, use the manual export option from the viewer.
```